State of the Practice for Lattice Boltzmann Method Software

### 2022-03-06 StateOfPractice/Papers/LatticeBoltz_SOP-arXiv/LatticeBoltz_SOP.tex
reviewed abstract and section 1

    We analyze the state of software development practice for Lattice Boltzmann
    solvers by quantitatively and qualitatively measuring and comparing 24
    software packages for 10 software qualities (installability, correctness/
    verifiability, reliability, robustness, usability, maintainability,
    reusability, understandability, visibility/transparency and
    reproducibility). Our reproducible analysis method employs a measurement
    template (containing 108 measures that are manually and automatically
    extracted from the project repository) and developer interviews (consisting
    of a set of 20 questions). From the measurement results, we ranked the
    software using the Analytic Hierarchy Process (AHP). Our ranking was roughly
    consistent with ranking the repositories by the number of GitHub stars,
    although the number one project by star count (Sailfish) is ranked 9th by
    our methodology. Our finding is that the state of the practice is healthy
    with 67\% of the measured packages ranking in the top 5 for at least one
    quality, the majority of LBM generated artifacts corresponding to general
    recommendations from research software developers, common utilization of
    version control (67\% of packages) and adoption of a quasi-agile development
    process.  Areas of best practice to potentially improve include adoption of
    continuous integration, API documentation and enforcement of programming
    style guides.  We interviewed 4 developers to gain insight into their
    current pain points. Identified challenges include lack of development time,
    lack of funding, and difficulty with ensuring correctness.  Developers are
    addressing these pain points by designing for change, circumventing the
    oracle problem and prioritizing documentation and usability.  For future the
    best practices, we suggest the community consider the following: employing
    linters, conducing rigorous peer reviews, writing and submitting more papers
    on software, growing the number of contributors and augmenting the theory
    manuals to include more requirements relevant information.

>>>>

    We analyze the state of software development practice for Lattice Boltzmann
    solvers by quantitatively and qualitatively measuring and comparing 24
    software packages for 10 software qualities (installability, correctness/
    verifiability, reliability, robustness, usability, maintainability,
    reusability, understandability, visibility/transparency and
    reproducibility). Our reproducible analysis method employs a measurement
    template (containing 108 measures that are manually and automatically
    extracted from the project repository) and developer interviews (consisting
    of a set of 20 questions). From the measurement results, we ranked the
    software using the Analytic Hierarchy Process (AHP). Our ranking was roughly
    consistent with ranking the repositories by the number of GitHub stars,
    although the number one project by star count (Sailfish) is ranked 9th by
    our methodology. Our finding is that the state of the practice is healthy
    with 67\% of the measured packages ranking in the top 5 for at least one
    quality, the majority of LBM generated artifacts corresponding to general
    recommendations from research software developers, common utilization of
    version control (67\% of packages) and adoption of a quasi-agile development
    process.  Areas of best practice to potentially improve include adoption of
    continuous integration, API documentation and enforcement of programming
    style guides.  We interviewed 4 developers to gain insight into their
    current pain points. Identified challenges include lack of development time,
    lack of funding, and difficulty with ensuring correctness.  Developers are
    addressing these pain points by designing for change, circumventing the
    oracle problem and prioritizing documentation and usability.  For future
    best practices, we suggest the community consider the following: employing
    linters, conducting rigorous peer reviews, writing and submitting more papers on software, growing the number of contributors and augmenting the theory manuals to include more requirements relevant information.
